Analysis for Project

### 2021-11-16 analysis/analysis.Rmd
Adjust models for sampling design
I use the survey library to adjust for the clustering of observations in households and to apply person weights. I also would like to apply the strata effects (because these can reduce SEs!) but currently svydesign is throwing up errors when I do.

design_matrix$race <- acs$race
design_matrix$below_exp_grade <- acs$below_exp_grade
```

Now, I can run the models. Warning, the code chunks below take a bit of time to run!

```{r build-models, results='asis'}
model0 <- glm(below_exp_grade~race, data=design_matrix, family=binomial)
model1 <- update(model0, 
                 .~.+y2011+y2012+y2013+y2014+y2015+y2016+y2017+y2018+y2019+
                   current_grade1st+current_grade2nd+current_grade3rd+
                   current_grade4th+current_grade5th+current_grade6th+
                   current_grade7th+current_grade8th+current_grade9th+
                   current_grade10th+current_grade11th+current_grade10th+
                   current_grade11th+current_grade12th+
                   met_non_metro+met_central_city+met_non_central_city+
                   met_city_indeter+
                   s1+s2+s3+s4+s5+s6+s7+s8+s9+s10+s11+s12+s13+s14+s15+s16+s17+
                   s18+s19+s20+s21+s22+s23+s24+s25+s26+s27+s28+s29+s30+s31+s32+
                   s33+s34+s35+s36+s37+s38+s39+s40+s41+s42+s43+s44+s45+s46+s47+
                   s48+s49+s50)
model2 <- update(model1, .~.+foreign_born+foreign_born_mother+
                   foreign_born_father)
model3 <- update(model2, .~.+degree_motherHS+degree_motherAA+degree_motherBA+
                   degree_motherG+degree_fatherHS+degree_fatherAA+
                   degree_fatherBA+degree_fatherG)
model4 <- update(model3, .~.+income_trans+own_home+parents_married)

@@

g+annotate("text", 1, 0.037, hjust="left",
             label="Grey bands give 83%\nconfidence interval around\nmonoracial estimates")+
  annotate("text", 2, 0.0475, hjust="left",
             label="Red band gives 83%\nconfidence interval around\nmidpoint estimate")+
  annotate("text", 2.5, 0.038, hjust="left",
             label="Actual biracial estimate\nshown with 83% confidence\ninterval")
```

>>>>

design_matrix$race <- acs$race
design_matrix$below_exp_grade <- acs$below_exp_grade

# add design effects
design_matrix$cluster <- acs$cluster
design_matrix$strata <- acs$strata
design_matrix$perwt <- acs$perwt

#TODO: It won't let me add strata - gives some error. This sucks because 
#strata may help to reduce SEs
design_matrix <- svydesign(ids=~cluster, weights=~perwt, data=design_matrix)

```

Now, I can run the models. I am using the `svyglm` command which (given the design set up above) adjusts for clustering and weights observations based on sample weights. I also want to figure out how to adjust for strata, but `svydesign` is throwing up errors when I attemp to do that. Warning, the code chunks below take a bit of time to run!

```{r build-models, results='asis'}
model0 <- svyglm(below_exp_grade~race, design=design_matrix, family=binomial)
model1 <- update(model0, 
                 .~.+y2011+y2012+y2013+y2014+y2015+y2016+y2017+y2018+y2019+
                   current_grade1st+current_grade2nd+current_grade3rd+
                   current_grade4th+current_grade5th+current_grade6th+
                   current_grade7th+current_grade8th+current_grade9th+
                   current_grade10th+current_grade11th+current_grade10th+
                   current_grade11th+current_grade12th+
                   met_non_metro+met_central_city+met_non_central_city+
                   met_city_indeter+
                   s1+s2+s3+s4+s5+s6+s7+s8+s9+s10+s11+s12+s13+s14+s15+s16+s17+
                   s18+s19+s20+s21+s22+s23+s24+s25+s26+s27+s28+s29+s30+s31+s32+
                   s33+s34+s35+s36+s37+s38+s39+s40+s41+s42+s43+s44+s45+s46+s47+
                   s48+s49+s50)
model2 <- update(model1, .~.+foreign_born+foreign_born_mother+
                   foreign_born_father)
model3 <- update(model2, .~.+degree_motherHS+degree_motherAA+degree_motherBA+
                   degree_motherG+degree_fatherHS+degree_fatherAA+
                   degree_fatherBA+degree_fatherG)
model4 <- update(model3, .~.+income_trans+own_home+parents_married)

@@

g+annotate("text", 1, 0.0375, hjust="left",
             label="Grey bands give 83%\nconfidence interval around\nmonoracial estimates")+
  annotate("text", 2, 0.048, hjust="left",
             label="Red band gives 83%\nconfidence interval around\nmidpoint estimate")+
  annotate("text", 2.5, 0.039, hjust="left",
             label="Actual biracial estimate\nshown with 83% confidence\ninterval")
```
